Traditional agroforestry systems in Timor-Leste can store large amounts of carbon in both soil and biomass

### 2024-03-18 manuscript.Rmd
bootstrap values

```{r test-bd-pedotransfer}
# bulk density from pedotransfer function: Minasny and Hartemink, 2011

data_soil$depth_mean <- unlist(lapply(strsplit(data_soil$SAMPLE_DEPTH, "-"), function(x) mean(as.numeric(x))))
data_soil$depth_max <- unlist(lapply(strsplit(data_soil$SAMPLE_DEPTH, "-"), function(x) as.numeric(x[2])))

data_soil$sand <- as.numeric(data_soil$`FINE SAND`) + as.numeric(data_soil$`COARSE SAND`)/100

data_soil$BDmin <- 
  0.935 + 
  0.049 * log(data_soil$depth_mean) + 
  0.0055 * data_soil$sand + 
  0.000065 * (data_soil$sand - 38.96)^2

data_soil$BDptf <- 
  100/(
    data_soil$OM/0.224 + 
      (100 - data_soil$OM)/data_soil$BDmin
  )

# g1 = ggplot(data_soil, aes(x = BD, y = BDptf, color = ID_TYPE)) + 
#   geom_abline(slope = 1, intercept = 0, lty=2) + 
#   geom_point() + 
#   scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
#   lims(x = c(0.8, 1.6), y = c(0.8, 1.6)) +
#   facet_wrap(~ID_VILLAGE)
# #+
#   # theme(legend.position = "none")
# g2 = ggplot(data_soil, aes(x = BD, y = BDmin, color = SAMPLE_DEPTH)) +
#   geom_abline(slope = 1, intercept = 0, lty=2) + 
#   geom_point() + 
#   scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
#   lims(x = c(0.8, 1.6), y = c(0.8, 1.6)) +
#   theme(legend.position = c(0.2, 0.8))
# 
# ggpubr::ggarrange(g1, g2) 
# ggsave("figures/pedotransfer-test.png", height = 5, width = 10)
```

@@

```{r total-soc}
# calculate total soil carbon stock per depth
data_soil[, c("h0", "h1") := lapply(data.table::tstrsplit(SAMPLE_DEPTH, "-"), as.numeric)]
data_soil[, Cstock :=          ## in Mg/ha
            (h1 - h0) * 1e8 *  ## equivalent volume of a 1 ha soil sample, in cm3/ha
            BD *               ## bulk density 
            Corg/100 *         ## carbon organic content in soil
            (1-CF) *           ## remove coarse fraction
            1e-6               ## convert from g/ha to Mg/ha
]

data_soil_C <-
  data_soil[, .(
    meanSC = sum(Cstock),
    SC10 = Cstock[SAMPLE_DEPTH == "0-10"],
    clay = mean(as.numeric(CLAY), na.rm = TRUE)
  ), .(N_PLOT)]

@@

```{r soc-error-propagation}
## error propagation using a Monte Carlo method -------------
data_soil_unc = data_soil[, .(BD = rnorm(1000, BD, BD*0.1), 
                              Corg = rnorm(1000, Corg, Corg*0.12), 
                              CF = rnorm(1000, CF, CF*0.15), 
                              iter = 1:1000), 
                          .(N_PLOT, SAMPLE_DEPTH, h1, h0)]

data_soil_unc = data_soil_unc[, .(
  Cstock = sum(
    (h1 - h0) * 1e8 *  
      BD * Corg/100 * (1-CF) * 1e-6  
  ), 
  Cstock10 = (
    (h1 - h0) * 1e8 *  
      BD * Corg/100 * (1-CF) * 1e-6  
  )[SAMPLE_DEPTH == "0-10"]),
  .(N_PLOT, iter)
]

data_soil_unc = data_soil_unc[, .(
  lwrSC = quantile(Cstock, 0.025), 
  uprSC = quantile(Cstock, 0.975),
  lwrSC10 = quantile(Cstock10, 0.025), 
  uprSC10 = quantile(Cstock10, 0.975)), 
  .(N_PLOT)]
```

@@

# add soil carbon uncertainty
dataC <- merge(dataC, data_soil_unc, all=TRUE)

@@

```{r tab-mean, results = "show"}
# average values per village and SAF type
dataC_mean <- dataC[, .(AGC = paste0(round(mean(meanAGC[!is.na(meanAGC)]), 2), " +/- ", round(sd(meanAGC[!is.na(meanAGC)])/sqrt(length(meanAGC[!is.na(meanAGC)])), 2)), 
                        SC = paste0(round(mean(meanSC[!is.na(meanSC)]), 2), " +/- ", round(sd(meanSC[!is.na(meanSC)])/sqrt(length(meanSC[!is.na(meanSC)])), 2))),
                    .(ID_AF)]
dataC_mean$ID_AF <- factor(dataC_mean$ID_AF, levels = c("CF", "SP", "YA", "HG", "FG"))
dataC_mean = dataC_mean[order(dataC_mean$ID_AF),]
knitr::kable(dataC_mean, col.names = c("Agroforestry system", "Aboveground carbon (Mg/ha)", "Soil organic carbon (Mg/ha)"))
write.csv(dataC_mean, file = "tables/C_mean_SAF.csv", row.names = FALSE)
```

```{r group-comparison}

dataC[, ID_SUCO := substr(ID_VILLAGE, 1, 1)]
## test normality of the data

# log-transform data to get normal distributions (because strictly positive data)
hist((dataC$meanAGC), breaks = 20)
hist((dataC$meanSC))

# test normality
dataC[, .(
  shap.A = shapiro.test(log(meanAGC))$p.value, 
  shap.S = shapiro.test(log(meanSC))$p.value
  ), .(ID_AF, ID_SUCO)]
# levene test of homoscedasticity
library(car)
dataC[, leveneTest(log(meanAGC) ~ ID_AF*ID_SUCO)]$`Pr(>F)`[1]
dataC[, leveneTest(log(meanSC) ~ ID_AF*ID_SUCO)]$`Pr(>F)`[1]

@@

# # soc
# aovSOC = aov(meanSC ~ ID_AF, data = dataC)
# tuk <- glht(aovSOC, linfct = mcp(ID_AF = "Tukey"))
# summary(tuk)          # standard display
# tuk.cld <- cld(tuk)   # letter-based display
# 
# opar <- par(mai=c(1,1,1.5,1))
# plot(tuk.cld)

@@

```{r tab-anova, results = "show"}
# 2-way anova 
dataC[, ID_SUCO := substr(ID_VILLAGE, 1, 1)]
anov1 = anova(lm(log(meanAGC)~ID_SUCO+ID_AF, data = dataC))
anov2 = anova(lm(log(meanSC)~ID_SUCO+ID_AF, data = dataC))
tab_anov = data.frame(response = rep(c("AGC", "SOC"), each = 2), 
                      ind_var = rep(c("SUCO", "AF"), 2), 
                      p = round(c(anov1$`Pr(>F)`[1:2], anov2$`Pr(>F)`[1:2]), 3)
)

knitr::kable(tab_anov)
## non parametric 2 way anova: anova on ranks
# anov1 = anova(lm(rank(meanAGC)~ID_SUCO+ID_AF, data = dataC))
# anov2 = anova(lm(rank(meanSC)~ID_SUCO+ID_AF, data = dataC))
# tab_anov = data.frame(response = rep(c("AGC", "SOC"), each = 2), 
#                       ind_var = rep(c("SUCO", "AF"), 2), 
#                       p = round(c(anov1$`Pr(>F)`[1:2], anov2$`Pr(>F)`[1:2]), 3)
# )
```

@@

## Map of villages and plots with elevation
g2 = 
  ggplot(data = elevAll) +
  geom_raster(aes(x = x, y = y, fill=srtm_62_14)) +
  geom_point(data = data_plot, 
             aes(x = long, y = lat, color = ID_AF), size = 2) + 
  geom_point(data = data_plot, 
             aes(x = long, y = lat), shape = 1, size = 2) + 
  # coord_equal() +
  viridis::scale_fill_viridis(option = "D",
                              limits = range(c(elevS$srtm_62_14, elevG$srtm_62_14))
  ) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  labs(x = NULL, y = NULL, color = NULL, fill="Elevation (m)") +
  annotate(geom = "text", label = "b", x = -Inf, y = Inf, 
           hjust = -0.5, vjust = 1, fontface = "bold", size = 6) + 
  annotate(geom = "text", label = "c", x = Inf, y = -Inf, 
           hjust = 12, vjust = -9.8, fontface = "bold", size = 6) + 
  guides(color = FALSE, fill=guide_colorbar(title.position = "top")) +
  theme(legend.position = c(0.8, 0.85), legend.direction="horizontal", 
        axis.title = element_blank(), 
        axis.ticks = element_blank(), axis.text = element_blank(), 
        plot.title = element_text(hjust = 0.5), 
        panel.background = element_blank()) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))+
  ggspatial::annotation_scale() +
  coord_sf(crs = 'WGS84')

@@

```{r fig-2-barplot, fig.height = 5, fig.width = 6}
## melt data.table
dataC_all <- melt(dataC, id.vars = c("N_PLOT", "ID_VILLAGE", "ID_AF", "village"), 
                  measure.vars = c("meanAGC", "meanBGC", "meanSC"))

@@

dataC_all[, variable := factor(variable, levels = c("meanAGC", "meanBGC", "meanSC"))]
levels(dataC_all$variable) <- c("AGC", "BGC", "SOC")
dataC_all[, village := factor(village)]
levels(dataC_all$village) <- c("Gariuai", "Osso Luga")

@@

```{r tab-3-reg, results = "show"}
## mixed effect linear regression
lmeReg <- lmerTest::lmer(log(meanSC) ~ log(meanAGC) + (1|village), data = dataC)
# Nakagawa’s R2 for mixed models
R2 = performance::r2_nakagawa(lmeReg)
summary(lmeReg)

@@

```{r fig-3-reg, fig.height = 4, fig.width = 8}
dfpred = expand.grid(meanAGC = exp(seq(min(log(dataC$meanAGC), na.rm = TRUE),
                                       max(log(dataC$meanAGC), na.rm = TRUE),
                                       length.out = 20)),
                     depth = c("Soil depth: 0-30 cm", "Soil depth: 0-10 cm")) |>
  merge(dfreg[, c("depth", "intercept", "slope")], by = "depth")
setDT(dfpred)
dfpred[, meanSC := exp(intercept + slope * log(meanAGC))]

@@

# stack data for figure
dataC_30 = dataC[, c("N_PLOT", "village", "ID_AF",  "meanAGC", "lwrAGC", "uprAGC", "meanSC", "lwrSC", "uprSC")]
dataC_30$depth = "Soil depth: 0-30 cm"
dataC_10 = dataC[, c("N_PLOT", "village", "ID_AF",  "meanAGC", "lwrAGC", "uprAGC", "SC10", "lwrSC10", "uprSC10")]
dataC_10$depth = "Soil depth: 0-10 cm"
colnames(dataC_10) = colnames(dataC_30)
dataC_fig = rbind(dataC_10, dataC_30)

## figure
ggplot(dataC_fig, aes(color = ID_AF)) +
  geom_point(aes(x = meanAGC, y = meanSC, shape = village), size = 2) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (marg.) = '*", round(R2_marg, 3))),
            x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2, parse = TRUE, color = 1) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (cond.) = '*", round(R2_cond, 3))),
            x = -Inf, y = Inf, hjust = -0.1, vjust = 2.2, parse = TRUE, color = 1) +
  geom_linerange(aes(x = meanAGC, y = meanSC, ymin = lwrSC, ymax = uprSC)) +
  geom_errorbarh(aes(y = meanSC, xmin = lwrAGC, xmax = uprAGC)) +
  # geom_abline(data = dfreg, aes(intercept = intercept, slope = slope), lty = 2) +
  geom_line(data = dfpred, aes(x = meanAGC, y = meanSC), lty = 2, col = 1) +
  labs(color = "AFS", x = "AGC stocks (Mg C/ha)", y = "SOC stocks (Mg C/ha)", shape = "Site") +
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  # scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_x_log10() +
  scale_y_log10() +
  facet_wrap(~depth) +
  theme_classic()

@@

Total carbon stocks varied between `r dataC[, round(min(meanAGC + meanSC + meanBGC, na.rm = TRUE))]` and `r dataC[, round(max(meanAGC + meanSC + meanBGC, na.rm = TRUE))]` Mg C/ha, with an average of `r dataC[, round(mean(meanAGC + meanSC + meanBGC, na.rm = TRUE))]` Mg C/ha and a coefficient of variation of `r dataC[, round(100*sd(meanAGC + meanSC + meanBGC, na.rm = TRUE)/mean(meanAGC + meanSC + meanBGC, na.rm = TRUE))]`%  (Table 1; Figure 2). The AFS with the lowest total carbon stocks was the `r dataC[, mean(meanAGC + meanSC + meanBGC, na.rm = TRUE), .(ID_AF)][, ID_AF[which.min(V1)]]` with an average of `r dataC[, mean(meanAGC + meanSC + meanBGC, na.rm = TRUE), .(ID_AF)][, round(min(V1))]` Mg C/ha; the AFS with the highest total carbon stocks was the `r dataC[, mean(meanAGC + meanSC + meanBGC, na.rm = TRUE), .(ID_AF)][, ID_AF[which.max(V1)]]` with an average of `r dataC[, mean(meanAGC + meanSC + meanBGC, na.rm = TRUE), .(ID_AF)][, round(max(V1))]` Mg C/ha (Table 1; Figure 2).

@@

SOC stocks varied between `r dataC[, round(min(meanSC, na.rm = TRUE))]` and `r dataC[, round(max(meanSC, na.rm = TRUE))]` MgC/ha, with an average of `r dataC[, round(mean(meanSC, na.rm = TRUE))]` MgC/ha and a coefficient of variation of `r dataC[, round(100*sd(meanSC, na.rm = TRUE)/mean(meanSC, na.rm = TRUE))]`%  (Table 1; Figure 2). In disagreement with our hypothesis (H1b), no significant differences in SOC were observed between the five AFS studied (ANOVA p-value: `r tab_anov$p[tab_anov$response=="SOC" & tab_anov$ind_var == "AF"]`). However, the measured SOC stocks differed from suco to suco (ANOVA p-value: `r tab_anov$p[tab_anov$response=="SOC" & tab_anov$ind_var == "SUCO"]`; Table 2). The SOC stocks in Gariuai were on average higher (`r dataC[ID_SUCO=="G", round(mean(meanSC, na.rm = TRUE))]` Mg C/ha) than those in Osso Luga (`r dataC[ID_SUCO=="S", round(mean(meanSC, na.rm = TRUE))]` Mg C/ha; Figure 2).

@@

ggplot(data_soil[SAMPLE_DEPTH != "10-20"], aes(x = as.numeric(CLAY), y = Corg, col = SAMPLE_DEPTH)) +
  geom_point() +
  labs(col = "Soil depth (cm)", x = "Clay content (%)", y = "SOC content (%)") +
  scale_color_brewer(type = "qual") +
  # geom_smooth(method = "lm") +
  theme_classic()
ggsave("figures/fig-clay-corg.pdf", height = 4, width = 6)

ggplot(data_soil[SAMPLE_DEPTH != "10-20"], aes(x = as.numeric(CLAY) + as.numeric(`FINE SILT`), y = Corg, col = SAMPLE_DEPTH, shape = village)) +
  geom_point() +
  labs(col = "Soil depth (cm)", x = "Clay and fine silt content (%)", y = "SOC content (%)", shape = "Site") +
  scale_color_brewer(type = "qual") +
  # geom_smooth(method = "lm") +
  theme_classic()
ggsave("figures/fig-clay-silt-corg.png", height = 4, width = 6)
```

@@

```{r sfig-altitude}
dataCelev = merge(dataC[, c("N_PLOT", "meanSC", "uprSC", "lwrSC")], 
                 data_plot[, c("N_PLOT", "elev", "village")], by = "N_PLOT")

ggplot(dataCelev, aes(x = elev, y = meanSC, col = village)) +
  geom_pointrange(aes(ymin=lwrSC, ymax = uprSC)) + 
  theme_classic() +
  labs(x = "Elevation (m)", y = "SOC stocks (Mg C/ha)", col = "Site")
ggsave("figures/soc-elev.png", height = 4, width = 6)
```

@@

# simulation 100 values per plot, soil depth and variable with a 10% coefficient
# of variation (CV value from lab)
data_soil_plot_simu = 
  data_soil_plot[, .(
    value = rnorm(100, value, sd = 0.1*value), n = 1:100), 
    .(village, N_PLOT, SAMPLE_DEPTH, variable)]

>>>>

@@

```{r total-soc}
# calculate total soil carbon stock per depth
data_soil[, c("h0", "h1") := lapply(data.table::tstrsplit(SAMPLE_DEPTH, "-"), as.numeric)]
data_soil[, Cstock :=             ## in Mg/ha
            (h1 - h0) * 1e8 *     ## equivalent volume of a 1 ha soil sample, in cm3/ha
            Corg/100 *            ## carbon organic content in fine soil (unitless)
            (Sample_DRY * 1e-6) * ## mass of the fine fraction of the soil (Mg)
            (1/V_cylinder)        ## 1/volume of the cylinder, in cm-3
]

data_soil_C <-
  data_soil[, .(
    meanSOC = sum(Cstock),
    SC10 = Cstock[SAMPLE_DEPTH == "0-10"],
    clay = mean(as.numeric(CLAY), na.rm = TRUE)
  ), .(N_PLOT)]

@@

```{r soc-error-propagation}
## error propagation using a Monte Carlo method -------------
data_soil_unc = data_soil[, .(mass = rnorm(1000, Sample_DRY, Sample_DRY*0.1), 
                              Corg = rnorm(1000, Corg, Corg*0.12), 
                              iter = 1:1000), 
                          .(N_PLOT, SAMPLE_DEPTH, h1, h0)]

data_soil_unc = data_soil_unc[, .(
  Cstock = sum((h1 - h0) * 1e8 / 250 * Corg/100 * (mass * 1e-6)), 
  Cstock10 = ((h1 - h0) * 1e8 / 250 * Corg/100 * (mass * 1e-6))[SAMPLE_DEPTH == "0-10"]),
  .(N_PLOT, iter)
]

data_soil_quantile = data_soil_unc[, .(
  lwrSOC = quantile(Cstock, 0.025), 
  medSOC = quantile(Cstock10, 0.5),
  uprSOC = quantile(Cstock, 0.975),
  lwrSOC10 = quantile(Cstock10, 0.025), 
  medSOC10 = quantile(Cstock10, 0.5),
  uprSOC10 = quantile(Cstock10, 0.975)), 
  .(N_PLOT)]
```

@@

# add soil carbon uncertainty
dataC <- merge(dataC, data_soil_quantile, all=TRUE)

@@

```{r tab-median, results = "show"}

## bootstrapping

#1. prepare data
data_agc_boot = melt(data_agb_unc, 
                       measure.vars = c("AGC", "BGC"), 
                       id.vars = c("ID_VILLAGE", "N_PLOT", "ID_AF", "iter"))

data_soil_boot = data_soil_unc[, c("N_PLOT", "iter", "Cstock")]
colnames(data_soil_boot)[3] = "value"
data_soil_boot$variable = "SOC"
data_soil_boot$iter = paste0("V", data_soil_boot$iter)

data_soil_boot = merge(data_soil_boot, data_plot[, c("N_PLOT","ID_VILLAGE", "ID_AF")])

data_boot = rbind(data_agc_boot, data_soil_boot[, colnames(data_agc_boot), with = FALSE])

# 2. add total stocks
data_boot_tot = data_boot[, .(value = sum(value), variable = "TOT"), .(ID_VILLAGE, N_PLOT, ID_AF, iter)]
data_boot = rbind(data_boot, data_boot_tot[, colnames(data_boot), with = FALSE])

data_boot[, village := substr(ID_VILLAGE, 1, 1)]

# 3. bootstrap
data_boot_saf = data_boot[, .(value = mean(sample(value, length(value), replace = TRUE))),
    .(ID_AF, variable, iter)]

# calculate median and 95% confidence interval at site level
data_boot_saf  = data_boot_saf[, .(
  value = paste0(
  signif(mean(value), 3), " (",
  signif(quantile(value, 0.025), 3), "-", 
  signif(quantile(value, 0.975), 3), ")"
  )), 
  .(ID_AF, variable)]

data_boot_saf = dcast(data_boot_saf, ID_AF ~ variable, value = "value")

knitr::kable(data_boot_saf, col.names = c("Agroforestry system", "Aboveground carbon (MgC/ha)", "Belowground carbon (MgC/ha)", "Soil organic carbon (MgC/ha)", "Total carbon (MgC/ha)"))
write.csv(data_boot_saf, file = "tables/C_median_SAF.csv", row.names = FALSE)
```

```{r group-comparison}
dataC[, ID_SUCO := substr(ID_VILLAGE, 1, 1)]
## test normality of the data

# log-transform data to get normal distributions (because strictly positive data)
hist((dataC$meanAGC), breaks = 20)
hist((dataC$meanSOC))

# test normality
dataC[, .(
  shap.A = shapiro.test(log(medAGC))$p.value, 
  shap.S = shapiro.test(log(medSOC))$p.value
  ), .(ID_AF, ID_SUCO)]
# levene test of homoscedasticity
library(car)
dataC[, leveneTest(log(medAGC) ~ ID_AF*ID_SUCO)]$`Pr(>F)`[1]
dataC[, leveneTest(log(medSOC) ~ ID_AF*ID_SUCO)]$`Pr(>F)`[1]

@@

# # soc
# aovSOC = aov(meanSOC ~ ID_AF, data = dataC)
# tuk <- glht(aovSOC, linfct = mcp(ID_AF = "Tukey"))
# summary(tuk)          # standard display
# tuk.cld <- cld(tuk)   # letter-based display
# 
# opar <- par(mai=c(1,1,1.5,1))
# plot(tuk.cld)

@@

```{r tab-anova, results = "show"}
# 2-way anova 
dataC[, ID_SUCO := substr(ID_VILLAGE, 1, 1)]
anov1 = anova(lm(log(medAGC)~ID_SUCO+ID_AF, data = dataC))
anov2 = anova(lm(log(medSOC)~ID_SUCO+ID_AF, data = dataC))
tab_anov = data.frame(response = rep(c("AGC", "SOC"), each = 2), 
                      ind_var = rep(c("SUCO", "AF"), 2), 
                      p = round(c(anov1$`Pr(>F)`[1:2], anov2$`Pr(>F)`[1:2]), 3)
)

knitr::kable(tab_anov)
write.csv(tab_anov, file = "tables/anov.csv", row.names = FALSE)

## non parametric 2 way anova: anova on ranks
# anov1 = anova(lm(rank(meanAGC)~ID_SUCO+ID_AF, data = dataC))
# anov2 = anova(lm(rank(meanSOC)~ID_SUCO+ID_AF, data = dataC))
# tab_anov = data.frame(response = rep(c("AGC", "SOC"), each = 2), 
#                       ind_var = rep(c("SUCO", "AF"), 2), 
#                       p = round(c(anov1$`Pr(>F)`[1:2], anov2$`Pr(>F)`[1:2]), 3)
# )

@@

## Map of villages and plots with elevation
g2 = 
  ggplot(data = elevAll) +
  geom_raster(aes(x = x, y = y, fill=srtm_62_14)) +
  geom_point(data = data_plot, 
             aes(x = long, y = lat, color = ID_AF), size = 2) + 
  geom_point(data = data_plot, 
             aes(x = long, y = lat), shape = 1, size = 2) + 
  # coord_equal() +
  # viridis::scale_fill_viridis(option = "D",
  #                             limits = range(c(elevS$srtm_62_14, elevG$srtm_62_14))
  # ) +
  scale_fill_gradientn(colours = terrain.colors(10)) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  labs(x = NULL, y = NULL, color = NULL, fill="Elevation (m)") +
  annotate(geom = "text", label = "b", x = -Inf, y = Inf, 
           hjust = -0.5, vjust = 1, fontface = "bold", size = 6) + 
  annotate(geom = "text", label = "c", x = Inf, y = -Inf, 
           hjust = 12, vjust = -9.8, fontface = "bold", size = 6) + 
  guides(color = FALSE, fill=guide_colorbar(title.position = "top")) +
  theme(legend.position = c(0.8, 0.85), legend.direction="horizontal", 
        axis.title = element_blank(),
        # axis.ticks = element_blank(), axis.text = element_blank(), 
        plot.title = element_text(hjust = 0.5), 
        panel.background = element_blank()) +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0))+
  ggspatial::annotation_scale() +
  coord_sf(crs = 'WGS84')

@@

```{r fig-2-barplot, fig.height = 5, fig.width = 6}
## melt data.table
dataC_all <- melt(dataC, id.vars = c("N_PLOT", "ID_VILLAGE", "ID_AF", "village"), 
                  measure.vars = c("meanAGC", "meanBGC", "meanSOC"))

@@

dataC_all[, variable := factor(variable, levels = c("meanAGC", "meanBGC", "meanSOC"))]
levels(dataC_all$variable) <- c("AGC", "BGC", "SOC")
dataC_all[, village := factor(village)]
levels(dataC_all$village) <- c("Gariuai", "Osso Luga")

@@

```{r tab-3-reg, results = "show"}
## mixed effect linear regression
lmeReg <- lmerTest::lmer(log(meanSOC) ~ log(meanAGC) + (1|village), data = dataC)
# Nakagawa’s R2 for mixed models
R2 = performance::r2_nakagawa(lmeReg)
summary(lmeReg)

@@

```{r fig-3-reg, fig.height = 4, fig.width = 8}
dfpred = expand.grid(meanAGC = exp(seq(min(log(dataC$meanAGC), na.rm = TRUE),
                                       max(log(dataC$meanAGC), na.rm = TRUE),
                                       length.out = 20)),
                     depth = c("Soil depth: 0-30 cm", "Soil depth: 0-10 cm")) |>
  merge(dfreg[, c("depth", "intercept", "slope")], by = "depth")
setDT(dfpred)
dfpred[, meanSOC := exp(intercept + slope * log(meanAGC))]

@@

# stack data for figure
dataC_30 = dataC[, c("N_PLOT", "village", "ID_AF",  "meanAGC", "lwrAGC", "uprAGC", "meanSOC", "lwrSOC", "uprSOC")]
dataC_30$depth = "Soil depth: 0-30 cm"
dataC_10 = dataC[, c("N_PLOT", "village", "ID_AF",  "meanAGC", "lwrAGC", "uprAGC", "SC10", "lwrSOC10", "uprSOC10")]
dataC_10$depth = "Soil depth: 0-10 cm"
colnames(dataC_10) = colnames(dataC_30)
dataC_fig = rbind(dataC_10, dataC_30)

## figure
ggplot(dataC_fig, aes(color = ID_AF)) +
  geom_point(aes(x = meanAGC, y = meanSOC, shape = village), size = 2) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (marg.) = '*", round(R2_marg, 3))),
            x = -Inf, y = Inf, hjust = -0.1, vjust = 1.2, parse = TRUE, color = 1) +
  geom_text(data = dfreg, aes(label = paste0("R^{2}*' (cond.) = '*", round(R2_cond, 3))),
            x = -Inf, y = Inf, hjust = -0.1, vjust = 2.2, parse = TRUE, color = 1) +
  geom_linerange(aes(x = meanAGC, y = meanSOC, ymin = lwrSOC, ymax = uprSOC)) +
  geom_errorbarh(aes(y = meanSOC, xmin = lwrAGC, xmax = uprAGC)) +
  # geom_abline(data = dfreg, aes(intercept = intercept, slope = slope), lty = 2) +
  geom_line(data = dfpred, aes(x = meanAGC, y = meanSOC), lty = 2, col = 1) +
  labs(color = "AFS", x = "AGC stocks (Mg C/ha)", y = "SOC stocks (Mg C/ha)", shape = "Site") +
  expand_limits(x = 0, y = 0) +
  scale_color_manual(values = RColorBrewer::brewer.pal(n = 6, name = 'Dark2')[-5]) +
  # scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  scale_x_log10() +
  scale_y_log10() +
  facet_wrap(~depth) +
  theme_classic()

@@

Total carbon stocks varied between `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT)][,round(min(V1))]` and `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT)][,round(max(V1))]` Mg C/ha, with an average of `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT)][,round(mean(V1))]` Mg C/ha and a coefficient of variation of `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT)][,round(sd(V1)/mean(V1)*100)]`%  (Table 1; Figure 2). The AFS with the lowest total carbon stocks was the `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT,ID_AF)][, ID_AF[which.min(V1)]]` with a median of `r data_boot_tot[variable=="TOT", mean(value), .(N_PLOT,ID_AF)][, round(min(V1))]` Mg C/ha; the AFS with the highest total carbon stocks was the `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT,ID_AF)][, ID_AF[which.max(V1)]]` with a median of `r data_boot_tot[variable=="TOT", median(value), .(N_PLOT,ID_AF)][, round(max(V1))]` Mg C/ha (Table 1; Figure 2).

@@

SOC stocks varied between `r dataC[, round(min(meanSOC, na.rm = TRUE))]` and `r dataC[, round(max(meanSOC, na.rm = TRUE))]` MgC/ha, with an average of `r dataC[, round(mean(meanSOC, na.rm = TRUE))]` MgC/ha and a coefficient of variation of `r dataC[, round(100*sd(meanSOC, na.rm = TRUE)/mean(meanSOC, na.rm = TRUE))]`%  (Table 1; Figure 2). In disagreement with our hypothesis (H1b), no significant differences in SOC were observed between the five AFS studied (ANOVA p-value: `r tab_anov$p[tab_anov$response=="SOC" & tab_anov$ind_var == "AF"]`). However, the measured SOC stocks differed from suco to suco (ANOVA p-value: `r tab_anov$p[tab_anov$response=="SOC" & tab_anov$ind_var == "SUCO"]`; Table 2). The SOC stocks in Gariuai were on average higher (`r dataC[ID_SUCO=="G", round(mean(meanSOC, na.rm = TRUE))]` Mg C/ha) than those in Osso Luga (`r dataC[ID_SUCO=="S", round(mean(meanSOC, na.rm = TRUE))]` Mg C/ha; Figure 2).

@@

ggplot(data_soil[SAMPLE_DEPTH != "10-20"], aes(x = as.numeric(CLAY), y = Corg, col = SAMPLE_DEPTH)) +
  geom_point() +
  labs(col = "Soil depth (cm)", x = "Clay content (%)", y = "SOC content (%)") +
  scale_color_brewer(type = "qual") +
  scale_x_log10() + 
  scale_y_log10() +
  geom_smooth(method = "lm") +
  theme_classic()
ggsave("figures/fig-clay-corg.pdf", height = 4, width = 6)

lmerTest::lmer(
  log(Corg) ~ log(as.numeric(CLAY) + as.numeric(`FINE SILT`)) + 
     (1|village)+ 
     (1|SAMPLE_DEPTH), 
   data = data_soil[SAMPLE_DEPTH != "10-20"]) |> 
  summary()

ggplot(data_soil[SAMPLE_DEPTH != "10-20"], aes(x = as.numeric(CLAY) + as.numeric(`FINE SILT`), y = Corg, col = SAMPLE_DEPTH, shape = village)) +
  geom_point() +
  labs(col = "Soil depth (cm)", x = "Clay and fine silt content (%)", y = "SOC content (%)", shape = "Site") +
  scale_color_brewer(type = "qual") +
  # scale_x_log10() +
  # scale_y_log10() +
  # geom_smooth(method = "lm") +
  theme_classic()
ggsave("figures/fig-clay-silt-corg.png", height = 4, width = 6)
```

@@

```{r sfig-altitude}
dataCelev = merge(dataC[, c("N_PLOT", "meanSOC", "uprSOC", "lwrSOC")], 
                 data_plot[, c("N_PLOT", "elev", "village")], by = "N_PLOT")

lmerTest::lmer(log(meanSOC) ~ log(elev) + (1|village), data = dataCelev) |> 
  summary()

ggplot(dataCelev, aes(x = elev, y = meanSOC, col = village)) +
  geom_pointrange(aes(ymin=lwrSOC, ymax = uprSOC)) + 
  theme_classic() +
  labs(x = "Elevation (m)", y = "SOC stocks (Mg C/ha)", col = "Site")
ggsave("figures/soc-elev.png", height = 4, width = 6)
```

@@

# simulation 100 values per plot, soil depth and variable with a 12% coefficient
# of variation (CV value from lab)
data_soil_plot_simu = 
  data_soil_plot[, .(
    value = rnorm(100, value, sd = 0.12*value), n = 1:100), 
    .(village, N_PLOT, SAMPLE_DEPTH, variable)]
